### 2022-11-29 dissertation/chapters/08-results.tex
🚧 (final-review): Chapter 8 WIP

The last step in the scientific process requires the presentation of the outcomes of the empirical process. Objective discussions based on statistical analysis of the findings is required. The design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}. The methodology presented a number of experimental groups to conduct. The experimental groups that were identified include a case study on the behaviour of the \acs{BHH} during training, an empirical comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics, and a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.

This chapter provides the outcomes of the empirical processes and provides results on all the experiments that have been conducted. Detailed discussions follow on the outcomes of each experiment. Discussions are accompanied by figures and plots to help provide visual aid for discussions. The output of the statistical analysis that yielded the results is provided in Appendix~\ref{app:statistical_analysis}. The remainder of the chapter is structured as follows.

@@

This section provides a brief discussion on the general outcome of the empirical process as a whole. Overall the \acs{BHH} is shown to successfully train the underlying \acp{FFNN} for all datasets. In general, the \acs{BHH} performs well and the empirical process provides key insights into the workings of the \acs{BHH}. Where possible, a number of improvements to the \acs{BHH} are identified and recommended as it relates to the outcomes of the results.

@@

All of the underlying \acp{FFNN} trained in the empirical process are relatively small. As such, most of the training progress is observed to occur withing the first five epochs. As a result, the \acs{BHH} should apply most learning at the early stages of the training process. After five epochs, the training of most of the underlying \acp{FFNN} converges and little performance gain is observed after that point. Since this empirical process does not apply early stopping of the training process, the \acs{BHH} will continue to explore the \index{heuristic}heuristic space beyond the five epoch mark.

@@

These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards \index{heuristic}heuristics that perform well at all. This section is structured as follows.

@@

This section provides illustrations and discussions around the outcomes of the train and test performance metrics as obtained by the \acs{BHH}. Figures~\ref{fig:results:case_study:metrics:train_loss}-\ref{fig:results:case_study:metrics:test_accuracy} provide illustrations of the train and test, loss and accuracy plots of the \acs{BHH} over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_loss.pdf}
            \caption{Train log loss}
            \label{fig:results:case_study:metrics:train_loss}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_loss.pdf}
            \caption{Test log loss}
            \label{fig:results:case_study:metrics:test_loss}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_accuracy.pdf}
            \caption{Train log accuracy}
            \label{fig:results:case_study:metrics:train_accuracy}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_accuracy.pdf}
            \caption{Test log accuracy}
            \label{fig:results:case_study:metrics:test_accuracy}
      \end{subfigure}
      \par\bigskip
      \caption{The average train and test, loss and accuracy plots over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:metrics}
\end{figure}

@@

The volatility observed in Figure~\ref{fig:results:case_study:metrics:test_loss} is due to overfitting and partly due to the noisiness that results from mini-batch training. Early stopping can be applied to the training process to hault training before the model overfits on the training data. The training dataset is also very small, with just 120 samples. As such, overfitting can be expected.

@@

To illustrate the learning process undergone by the \acs{BHH}, further investigation is required. Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$. The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{probabilities of selection probabilities}. Figures~\ref{fig:results:case_study:alphas:0}-\ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at index 0, 6, 7, and 8 respectively. Index 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool. Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.

@@

The first logical observation to be made from Figures~\ref{fig:results:case_study:alphas:0}-\ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}. Since the replay window size is sufficienty large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all. The value for $\boldsymbol{\alpha}$ is never reset to its initial value of 1.0, and thus, $\boldsymbol{\alpha}$ continues to increase throughout the training process. However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$. The aforementioned observation is the first indicator of the learning process yielded by the \acs{BHH}. Heuristics that perform well will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly that other heuristics that do not perform well.

@@

Notice from Figure~\ref{fig:results:case_study:alphas} that $\boldsymbol{\alpha} \geq 1.0$ for multiple elements. This is due to the accumulation of pseudo counts for $\boldsymbol{\alpha}$ by the Bayesian analysis process. Furthermore, this is also because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1.0 to the corresponding element in $\boldsymbol{\alpha}$ through the Bayesian analysis process. In a case where all five entities in the entity pool are allocated the same heuristic, for all ten samples defined in the performance log, defined by the replay window size, $\alpha_{i} = 50$, where $i$ is the index of the $i$-th \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool.

Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning. The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurance} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$). \index{heuristic}Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequenctly reselect these \index{heuristic}heuristics again, or just by chance through the stochastic nature of probabilistic sampling as implemented by the \acs{BHH}. Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.

@@

Figures~\ref{fig:results:case_study:thetas:0}-\ref{fig:results:case_study:thetas:8} provide illustrations of the probabilities of the \index{heuristic}heuristic selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs. These illustrations are presented in log scale. Similar to what is previously mentioned, \textit{probabilities of selection probabilities} at index 0, 6, 7, and 8 represent the probabilities of \index{heuristic}heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the probabilities of selection probabilities in $\boldsymbol{\theta}$ and thus, the \index{heuristic pool}heuristic pool. Once again, simular illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.

@@

From the illustrations presented in Figures~\ref{fig:results:case_study:thetas:0}-\ref{fig:results:case_study:thetas:8}, a clearer picture off the learning process of the \acs{BHH} is formed. The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}. As a reminder, ten low-level \index{heuristic}heuristics are included in the heuristic pool, yielding an expected probability of \index{heuristic}heuristics selection probability of 0.1, for each \index{heuristic}heuristic, by the frequentist view of probabilistic modeling.

@@

Both the bhh\_baseline (\textcolor{red}{red}) and the bhh\_replay\_250 (\textcolor{green}{green}) configurations make use of the \textit{ibest} credit assignment strategy. The \textit{ibest} credit assignment strategy allocates credit to the heuristic that yield the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance. However, since the bhh\_baseline is configured with a small replay window size of 10, and a reanalysis interval of 10, the concentration parameter $\boldsymbol{\alpha}$ gets reset to its default value of 1.0 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is broader, and thus, explaining the larger variance of $\boldsymbol{\theta}$ throughout.

@@

It should be noted that, despite using the same random seed across configurations for the same run number, after about 30 steps, the behavioural changes between the configurations start the show. As a reminder, the bhh\_credit\_symmetric (\textcolor{blue}{blue}) configuration, does not bias towards best performing \index{heuristic}heuristics and thus, where the bhh\_baseline and bhh\_replay\_250 configurations diverge from the behaviour of the bhh\_credit\_symmetric configuration. The difference in behaviour is proof of the effect of performance bias.

@@

This section provides a brief investigation into the \textit{prior \index{heuristic}heuristic selection probabilities}, that result from the probabilistic model implemented by the \acs{BHH}. The prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.

Figures~\ref{fig:results:case_study:p_H:0}-\ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, sampled from the \index{heuristic}heuristic selection probability distribution $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at index 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs. Similar to before, these illustrations are also presented in log scale.

@@

The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the probabilities of \index{heuristic}heuristic selection probabilities presented in the previous section in Figure~\ref{fig:results:case_study:thetas}. This is because of the \textit{reselection} interval hyper-parameter. The reselection interval hyper-parameter is implemented as a way to control the frequency by which new heuristics are selected and allocated to each entity. Since the default \textit{reselection} interval is set to 10, the \index{heuristic}heuristic selection probabilities are only resampled at intervals of 10. These illustrations then simply yield rough approximations of the illustrations provided in Figures~\ref{fig:results:case_study:thetas:0}-\ref{fig:results:case_study:thetas:8} for the probabilities of \index{heuristic}heuristic selection probabilities. As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.

@@

Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior \index{heuristic}heuristic selection probabilities at index 0, 6, 7, and 8, throughout the training process, averaged over 30 runs. Similar to before, these illustrations are also presented in log scale. As before, illustrations for the other indices are left out for brevity as they yield simular illustrations.

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
            \caption{$P(h_{0} \vert e_{0}, c_{1})$ - \acs{SGD}}
            \label{fig:results:case_study:p_HgEC:0:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
            \caption{$P(h_{6} \vert e_{0}, c_{1})$ - \acs{Adam}}
            \label{fig:results:case_study:p_HgEC:0:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
            \caption{$P(h_{7} \vert e_{0}, c_{1})$ - \acs{PSO}}
            \label{fig:results:case_study:p_HgEC:0:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
            \caption{$P(h_{8} \vert e_{0}, c_{1})$ - \acs{GA}}
            \label{fig:results:case_study:p_HgEC:0:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average proportional posterior \index{heuristic}heuristic selection probabilities for \index{heuristic}heuristics $(\boldsymbol{H})$ at index 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy. The proportional posterior \index{heuristic}heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_HgEC:0}
\end{figure}

The main observation to make from Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8}, is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a \index{Categorical probability distribution}Categorical probability distribution from which new \index{heuristic}heuristic selections are sampled. The reasons for the aforementioned, is because the probablistic model, is evaluated proportionaly as was discussed in Chapter~\ref{chap:bhh}. As a reminder, the log-sum-exp trick is used in order to maintain numerical stability, yielding \textit{logits} instead of probabilities.

Another observation to make, is for the bhh\_replay\_250 configuration $(\textcolor{green}{green})$. From Figures~\ref{fig:results:case_study:p_HgEC:0:0}-\ref{fig:results:case_study:p_HgEC:0:8}, it can be seen that the posterior heuristic selection probabilities converge to the expected heuristic selection probabilities, later in the training stages. The aforementioned suggests that the \acs{BHH} is not able to find anymore performance biases and can not exploit better solutions. At this point, the \acs{BHH} starts to explore more as the concentration parameters are reanalysed more uniformly, resolving more and more to a random search in attempt to find better solutions.

Furthermore, the posterior heuristic selection probability distribution is conditional on the occurance of a specific entity that the potential \index{heuristic}heuristic will be applied to, as well as a specific performance criteria enforced by a specific credit assignment strategy. This means that \index{heuristic}heuristic selection is specific to each entity. A particular \index{heuristic}heuristic might be good for one entity, but not for another. This is a strong characteristic of the \acs{BHH}, as it learns to apply the correct \index{heuristic}heuristic to the correct entity at the correct time in the training process.

@@

From the observations made in Sections~\ref{sec:results:case_study:performance_metrics}-\ref{sec:results:case_study:posterior_selec_prob}, it can be concluded that the \acs{BHH} is able to successfully train the underlying \acs{FFNN} for the case study on the iris dataset. Furthermore it can be concluded that the learning mechanism implemented by the \acs{BHH} is able to exploit minor performance biases and thus, the \acs{BHH} is able to correctly allocate the correct heuristic to the correct entity at the correct time in the training process.

@@

From Table~\ref{tab:results:standalone:metrics:loss} it can be seen that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets. The bhh\_gd configuration managed to produce results that are comparable to the top three heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the \index{heuristic}heuristics.

@@

From Figure~\ref{fig:results:standalone:descriptive:descriptive} a few observations can be made. Firstly, both \acs{Adam} and \acs{RMSProp} achieved radically different average ranks for the student performance dataset, compared to the other datasets. This can also be see in Table~\ref{tab:results:standalone:metrics:rank}. Further investigation into the reasons for this is required as both these heuristics perform well on all other datasets, and the other heuristics perform well for the student performance dataset. A suggestions then leads to the possibility that an invalid learning rate or learning rate schedule leads to a scenario where good solutions are overshot, causing \acs{Adam} and \acs{RMSProp} to struggle to resolve back to good solutions. Furthermore, the bhh\_gd heuristic achieved the lowest variance in average rank across all datasets, compared to the other heuristics. The aforementioned shows the generalisation capabilities of the \acs{BHH} to multiple problems.

>>>>

The last step in the scientific process requires the presentation of the outcomes of the empirical process. Objective discussions based on statistical analysis of the findings are required. The design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}. The methodology presented a number of experimental groups to conduct. The experimental groups that were identified include a case study on the behaviour of the \acs{BHH} during training, an empirical comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics, and a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.

This chapter provides the outcomes of the empirical processes and provides results on all the experiments that have been conducted. Detailed discussions follow on the outcomes of each experiment. Discussions are accompanied by figures and plots to help provide visual aid for discussions. The output of the statistical analysis that yielded the results is provided in Appendix~\ref{app:statistical_analysis}. The remainder of the chapter is structured as follows:

@@

This section provides a brief discussion on the general outcome of the empirical process as a whole. Overall, the \acs{BHH} is shown to successfully train the underlying \acp{FFNN} for all datasets. In general, the \acs{BHH} performs well and the empirical process provides key insights into the workings of the \acs{BHH}. Where possible, a number of improvements to the \acs{BHH} are identified and recommended as it relates to the outcomes of the results.

@@

All of the underlying \acp{FFNN} trained in the empirical process are relatively small. As such, most of the training progress is observed to occur within the first five epochs. As a result, the \acs{BHH} should apply most learning at the early stages of the training process. After five epochs, the training of most of the underlying \acp{FFNN} converges and little performance gain is observed after that point. Since this empirical process does not apply early stopping of the training process, the \acs{BHH} will continue to explore the \index{heuristic}heuristic space beyond the five epoch mark.

@@

These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards \index{heuristic}heuristics that perform well at all. This section is structured as follows:

@@

This section provides illustrations and discussions around the outcomes of the train and test performance metrics as obtained by the \acs{BHH}. Figures~\ref{fig:results:case_study:metrics:train_loss} to \ref{fig:results:case_study:metrics:test_accuracy} provide illustrations of the train and test loss and accuracy plots of the \acs{BHH} over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_loss.pdf}
            \caption{Train log loss}
            \label{fig:results:case_study:metrics:train_loss}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_loss.pdf}
            \caption{Test log loss}
            \label{fig:results:case_study:metrics:test_loss}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_accuracy.pdf}
            \caption{Train log accuracy}
            \label{fig:results:case_study:metrics:train_accuracy}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_accuracy.pdf}
            \caption{Test log accuracy}
            \label{fig:results:case_study:metrics:test_accuracy}
      \end{subfigure}
      \par\bigskip
      \caption{The average train and test loss and accuracy plots over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:metrics}
\end{figure}

@@

The volatility and minor divergence of the test loss compared to the training loss, observed in Figure~\ref{fig:results:case_study:metrics:test_loss}, is due to overfitting and partly due to the noisiness that results from mini-batch training. Early stopping can be applied to the training process to halt training before the model overfits on the training data. The training dataset is also very small, with just 120 samples. Furthermore, a very small batch size of 16 is used. As such, noisiness and overfitting can be expected.

@@

To illustrate the learning process undergone by the \acs{BHH}, further investigation is required. Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$. The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{probabilities of selection probabilities}. Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively. Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool. Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.

@@

The first logical observation to be made from Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}. Since the replay window size is sufficienty large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all. The value for $\boldsymbol{\alpha}$ is never reset to its initial value of 1.0, and thus, $\boldsymbol{\alpha}$ continues to increase throughout the training process. However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$. The aforementioned observation is the first indicator of the learning process yielded by the \acs{BHH}. Heuristics that perform well will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly than other heuristics that do not perform well.

@@

Notice from Figure~\ref{fig:results:case_study:alphas} that $\boldsymbol{\alpha} \geq 1.0$ for multiple elements. This is due to the accumulation of pseudo counts for $\boldsymbol{\alpha}$ by the Bayesian analysis process. Furthermore, this is also because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1.0 to the corresponding element in $\boldsymbol{\alpha}$ through the Bayesian analysis process. Consider a case where all five entities in the entity pool are allocated the same heuristic and that a the replay window size of 10 is used. For all ten samples defined in the performance log, $\alpha_{i} = 50$, where $i$ is the index of the $i$-th \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool.

Furthermore, it is important to mention that a change in $\boldsymbol{\alpha}$ between reanalysis windows does not yet necessarily indicate that the \acs{BHH} is learning. The concentration parameter $\boldsymbol{\alpha}$ tracks the \textit{occurrence} of the random event of observing heuristics (denoted $\boldsymbol{{H}}$). \index{heuristic}Heuristics can be observed as a result of good performance, by which the \acs{BHH} then learns to frequenctly reselect these \index{heuristic}heuristics again, or just by chance through the stochastic nature of probabilistic sampling as implemented by the \acs{BHH}. Further investigation is required to illustrate the learning mechanism of the \acs{BHH}.

@@

Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} provide illustrations of the probabilities of the \index{heuristic}heuristic selection probabilities, sampled from the probability distribution $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$ throughout the training process, and averaged over all 30 runs. These illustrations are presented in log scale. Similar to what is previously mentioned, \textit{probabilities of selection probabilities} at indices 0, 6, 7, and 8 represent the probabilities of \index{heuristic}heuristic selection probabilities for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the probabilities of selection probabilities in $\boldsymbol{\theta}$ and thus, the \index{heuristic pool}heuristic pool. Once again, simular illustrations for the other elements in $\boldsymbol{\theta}$ are left out for brevity as they contain similar illustrations.

@@

From the illustrations presented in Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8}, a clearer picture of the learning process of the \acs{BHH} is formed. The first important observation to make is for the bhh\_replay\_250 configuration, presented in \textcolor{green}{green}. As a reminder, ten low-level \index{heuristic}heuristics are included in the heuristic pool, yielding an expected probability of \index{heuristic}heuristics selection probability of 0.1, for each \index{heuristic}heuristic, by the frequentist view of probabilistic modeling.

@@

Both the bhh\_baseline (\textcolor{red}{red}) and the bhh\_replay\_250 (\textcolor{green}{green}) configurations make use of the \textit{ibest} credit assignment strategy. The \textit{ibest} credit assignment strategy allocates credit to the heuristic that yield the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance. However, since the bhh\_baseline is configured with a small replay window size of 10, and a reanalysis interval of 10, the concentration parameter $\boldsymbol{\alpha}$ is reset to its default value of 1.0 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is broader, and thus, explaining the larger variance of $\boldsymbol{\theta}$ throughout.

@@

It should be noted that, despite using the same random seed across configurations for the same run number, the behavioural changes between the configurations start to show after about 30 steps. As a reminder, the bhh\_credit\_symmetric (\textcolor{blue}{blue}) configuration, does not bias towards best performing \index{heuristic}heuristics. Where the bhh\_baseline and bhh\_replay\_250 configurations then diverge from the behaviour of the bhh\_credit\_symmetric configuration is proof of the effect of performance bias.

@@

This section provides a brief investigation into the \textit{prior \index{heuristic}heuristic selection probabilities} that result from the probabilistic model implemented by the \acs{BHH}. The prior \index{heuristic}heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$.

Figures~\ref{fig:results:case_study:p_H:0} to \ref{fig:results:case_study:p_H:8} provide illustrations of the prior \index{heuristic}heuristic selection probabilities, sampled from the \index{heuristic}heuristic selection probability distribution $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8, throughout the training process, and averaged over all 30 runs. Similar to before, these illustrations are also presented in log scale.

@@

The main observation to make from these figures is that they are much less volatile and noisy than the figures presented for the probabilities of \index{heuristic}heuristic selection probabilities presented in the previous section in Figure~\ref{fig:results:case_study:thetas}. This is because of the \textit{reselection} interval hyper-parameter. The reselection interval hyper-parameter is implemented as a way to control the frequency by which new heuristics are selected and allocated to each entity. Since the default \textit{reselection} interval is set to 10, the \index{heuristic}heuristic selection probabilities are only resampled at intervals of 10. These illustrations then simply yield rough approximations of the illustrations provided in Figures~\ref{fig:results:case_study:thetas:0} to \ref{fig:results:case_study:thetas:8} for the probabilities of \index{heuristic}heuristic selection probabilities. As such, the same observations and conclusions that are made in Section \ref{sec:results:case_study:probs_of_select_probs} also apply in this section.

@@

Figures~\ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} provide illustrations of the calculated posterior \index{heuristic}heuristic selection probabilities at indices 0, 6, 7, and 8, throughout the training process, averaged over 30 runs. Similar to before, these illustrations are also presented in log scale. As before, illustrations for the other indices are left out for brevity as they yield simular illustrations.

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
            \caption{$P(h_{0} \vert e_{0}, c_{1})$ - \acs{SGD}}
            \label{fig:results:case_study:p_HgEC:0:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
            \caption{$P(h_{6} \vert e_{0}, c_{1})$ - \acs{Adam}}
            \label{fig:results:case_study:p_HgEC:0:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
            \caption{$P(h_{7} \vert e_{0}, c_{1})$ - \acs{PSO}}
            \label{fig:results:case_study:p_HgEC:0:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
            \caption{$P(h_{8} \vert e_{0}, c_{1})$ - \acs{GA}}
            \label{fig:results:case_study:p_HgEC:0:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average proportional posterior \index{heuristic}heuristic selection probabilities for \index{heuristic}heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy. The proportional posterior \index{heuristic}heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert e_{0}, \gamma_{1})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_HgEC:0}
\end{figure}

The main observation to make from Figures~\ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} is that the implemented posterior heuristic selection distribution, defined by $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, does not yield normalised probabilities, but rather yield unnormalised \textit{logits}, which are used to parameterise a \index{Categorical probability distribution}Categorical probability distribution from which new \index{heuristic}heuristic selections are sampled. The reasons for the aforementioned is because the probablistic model is evaluated proportionaly as was discussed in Chapter~\ref{chap:bhh}. As a reminder, the log-sum-exp trick is used in order to maintain numerical stability, yielding \textit{logits} instead of probabilities.

Another observation to make is for the bhh\_replay\_250 configuration $(\textcolor{green}{green})$. Figures~\ref{fig:results:case_study:p_HgEC:0:0} to \ref{fig:results:case_study:p_HgEC:0:8} show that the posterior heuristic selection probabilities converge to the expected heuristic selection probabilities later in the training stages. The aforementioned suggests that the \acs{BHH} is not able to find anymore performance biases and cannot exploit better solutions. At this point, the \acs{BHH} starts to explore more as the concentration parameters are reanalysed more uniformly, resolving more and more to a random search in attempt to find better solutions.

Furthermore, the posterior heuristic selection probability distribution is conditional on the occurrence of a specific entity that the potential \index{heuristic}heuristic will be applied to, as well as a specific performance criterion enforced by a specific credit assignment strategy. This means that \index{heuristic}heuristic selection is specific to each entity. A particular \index{heuristic}heuristic might be good for one entity, but not for another. This is a strong characteristic of the \acs{BHH}, as it learns to apply the correct \index{heuristic}heuristic to the correct entity at the correct time in the training process.

@@

It can be concluded from Sections~\ref{sec:results:case_study:performance_metrics} to \ref{sec:results:case_study:posterior_selec_prob} that the \acs{BHH} is able to successfully train the underlying \acs{FFNN} for the case study on the iris dataset. Furthermore it can be concluded that the learning mechanism implemented by the \acs{BHH} is able to exploit minor performance biases, and thus the \acs{BHH} is able to correctly allocate the correct heuristic to the correct entity at the correct time in the training process.

@@

Table~\ref{tab:results:standalone:metrics:loss} shows that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets. The bhh\_gd configuration managed to produce results that are comparable to the top three heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the \index{heuristic}heuristics.

@@

From Figure~\ref{fig:results:standalone:descriptive:descriptive} a few observations can be made. Firstly, both \acs{Adam} and \acs{RMSProp} achieved radically different average ranks for the student performance dataset, compared to the other datasets. This can also be seen in Table~\ref{tab:results:standalone:metrics:rank}. Further investigation into the reasons for this is required as both these heuristics perform well on all other datasets, and the other heuristics perform well for the student performance dataset. A suggestion is that an invalid learning rate or learning rate schedule leads to a scenario where good solutions are overshot, causing \acs{Adam} and \acs{RMSProp} to struggle to resolve back to good solutions. Furthermore, the bhh\_gd heuristic achieved the lowest variance in average rank across all datasets, compared to the other heuristics. The aforementioned shows the generalisation capabilities of the \acs{BHH} to multiple problems.
